### 2022-06-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@19dcaf28f6830ab06f98bf10806dff89566caacf 🚀

Most previous work has assumed that coronavirus biogeography is driven
by coevolutionary regimes that form at finer taxonomic scales, treating
the presence or richness of key bat host groups as predictive of these
viruses' distribution.\textsuperscript{2,3} Projecting bat and
betacoronavirus phylogeny over space (fig.~\ref{fig:biogeo}), we find
further support for the idea that bat community assembly is directly
responsible for spatial heterogeneity in viral coevolutionary regimes.
The distinct groupings (represented by different colors, symbolizing
positions in a subspace formed by the first two phylogenetic principal
components) are essentially equivalent between the two groups, and can
be coarsely delineated as (1) south and southeast Asia, (2) east Asia
(including northern China), west Asia, and the Mediterranean coast; (3)
Eurasia above a northing of 40; and (4) Africa and south America. In
some cases, this diverges from expectations about coronavirus
biogeography: for example, previous work has rarely flagged India as a
region of concern, but for both bats and betacoronaviruses, the
subcontinent falls into the same phylogeographic regions as the
southeast Asian peninsula (and indeed, the region is home to known bat
hosts of nobecoviruses, sarbecoviruses, and merbecoviruses
{[}Ruiz-Aravena2022EcoEvo{]}).

>>>>

Most previous work has assumed that coronavirus biogeography is driven
by coevolutionary regimes that form at finer taxonomic scales, treating
the presence or richness of key bat host groups as predictive of these
viruses' distribution.\textsuperscript{2,3} Projecting bat and
betacoronavirus phylogeny over space (fig.~\ref{fig:biogeo}), we find
further support for the idea that bat community assembly is directly
responsible for spatial heterogeneity in viral coevolutionary regimes.
The distinct groupings (represented by different colors, symbolizing
positions in a subspace formed by the first two phylogenetic principal
components) are essentially equivalent between the two groups, and can
be coarsely delineated as (1) south and southeast Asia, (2) east Asia
(including northern China), west Asia, and the Mediterranean coast; (3)
Eurasia above a northing of 40; and (4) Africa and south America. In
some cases, this diverges from expectations about coronavirus
biogeography: for example, previous work has rarely flagged India as a
region of concern, but for both bats and betacoronaviruses, the
subcontinent falls into the same phylogeographic regions as the
southeast Asian peninsula (and indeed, the region is home to known bat
hosts of nobecoviruses, sarbecoviruses, and
merbecoviruses).\textsuperscript{3}
